Distributed Version Control Systems

### 2010-04-27 paper.tex
Modificada otras oraciones en More Atomical Commits

Many little commits, if needed, can be grouped as a bigger, conceptual commit.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions
(this also makes commits easier).

>>>>

Many little commits, if needed, can be grouped as a bigger, conceptual commit.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch back to the trunk. But creating and merging branches all the time is 
not effortless, and branches can be seen by everybody that has access to the repository, 
so this is not always done.

Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions
(this also makes commits easier).
